Precise predictions for same-sign W-boson scattering at the LHC

### 2018-02-21 Draft/description.tex
some minor changes, some comments by BJ incorporated in input.tex

  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
        Frederix:2016rdc}) for regulating IR singularities. The computations of one-loop amplitudes are carried out by switching dynamically between
        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which
        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
        Hirschi:2016mdz}, {\sc IREGI}~\cite{ShaoIREGI}, or {\sc Collier}~\cite{Denner:2016kdg}, together with an in-house 
        implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}. Finally, scale and PDF uncertainties can be obtained in an exact manner via reweigthing
        at zero additional CPU cost~\cite{Frederix:2011ss}.\\
        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
\begin{verbatim}
> set complex_mass_scheme #1
> import model loop_qcd_qed_sm_Gmu #2
> generate p p > e+ ve mu+ vm j j QCD=0 [QCD] #3
> output #4
\end{verbatim}
  With these commands the complex-mass scheme is turned on {\tt \#1}, then the NLO-capable model is loaded {\tt \#2}\footnote{Despite
            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections
        with the current version of the code.}, finally the process code is generated {\tt \#3} (note the {\tt QCD=0} syntax to select the purely-electroweak process)
        and written to disk {\tt \#4}. No approximation is performed for the Born and real-emission matrix elements. 
        For what concerns the virtual matrix element, because of some internal limitations which will be lifted in the future version capable of computing both QCD and EW corrections,
        only loops with QCD-interacting particles are generated. Such an approximation is equivalent to the assumption that the finite part of
        those loops which feature EW bosons is zero. In practice, since a part of the contribution to the single pole is also missing, the internal 
        pole-cancelation check at run time has to be turned off, by setting the value of the {\tt IR\-Pole\-Check\-Threshold} and 
        {\tt Precision\-Virtual\-At\-Run\-Time} parameters in the {\tt Cards/FKS\_params.dat} file to -1.
        {\bf MZ what exactly needs to be clarified here? perhaps I am just too used to this that I do not see problems here}

>>>>

  \item {\sc MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca} is an automatic meta-code (a code that generates codes) which makes it possible to simulate any scattering process
      including NLO QCD corrections both at fixed order and including matching to parton showers. It makes use of the FKS subtraction method~\cite{Frixione:1995ms,
        Frixione:1997np} (automated in the module {\sc MadFKS}~\cite{Frederix:2009yq,
        Frederix:2016rdc}) for regulating IR singularities. The computations of one-loop amplitudes are carried out by switching dynamically between
        two integral-reduction techniques, OPP~\cite{Ossola:2006us} or Laurent-series expansion~\cite{Mastrolia:2012bu},
        and TIR~\cite{Passarino:1978jh,Davydychev:1991va,Denner:2005nn}. These have been automated in the module {\sc MadLoop}~\cite{Hirschi:2011pa}, which
        in turn exploits {\sc CutTools}~\cite{Ossola:2007ax}, {\sc Ninja}~\cite{Peraro:2014cba,
        Hirschi:2016mdz}, {\sc IREGI}~\cite{ShaoIREGI}, or {\sc Collier}~\cite{Denner:2016kdg}, together with an in-house 
        implementation of the {\sc OpenLoops} optimisation~\cite{Cascioli:2011va}. Finally, scale and PDF uncertainties can be obtained in an exact manner via reweigthing
        at zero additional CPU cost~\cite{Frederix:2011ss}.\\
        The simulation of VBS at NLO-QCD accuracy can be performed by issuing the following commands in the program interface:
\begin{verbatim}
> set complex_mass_scheme
> import model loop_qcd_qed_sm_Gmu
> generate p p > e+ ve mu+ vm j j QCD=0 [QCD]
> output
\end{verbatim}
  With these commands the complex-mass scheme is turned on, then the NLO-capable model is loaded,\footnote{Despite
            the {\tt loop\_qcd\_qed\_sm\_Gmu} model also includes NLO counterterms for computing electro-weak corrections, it is not yet possible to compute such corrections
        with the current version of the code.} finally the process code is generated (note the {\tt QCD=0} syntax to select the purely-electroweak process)
        and written to disk. No approximation is performed for the Born and real-emission matrix elements. 
        For what concerns the virtual matrix element, because of some internal limitations which will be lifted in the future version capable of computing both QCD and EW corrections,
        only loops with QCD-interacting particles are generated. Such an approximation is equivalent to the assumption that the finite part of
        those loops which feature EW bosons is zero. In practice, since a part of the contribution to the single pole is also missing, the internal 
        pole-cancelation check at run time has to be turned off, by setting the value of the {\tt IR\-Pole\-Check\-Threshold} and 
        {\tt Precision\-Virtual\-At\-Run\-Time} parameters in the {\tt Cards\-/FKS\_\-params.dat} file to -1.
        {\bf MZ what exactly needs to be clarified here? perhaps I am just too used to this that I do not see problems here}

### 2018-02-21 Draft/input.tex
some minor changes, some comments by BJ incorporated in input.tex

The renormalisation and factorisation scales are set to the dynamical scale
%
\begin{equation}
\label{eq:defscale}
 \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}}, 
\end{equation}
%
\BJ{defined via the transverse momenta of the two hardest identified jets. } 
This choice of scale has been shown to provide stable NLO-QCD predictions \cite{Denner:2012dz}.

@@

\begin{itemize}
    \item The two same-sign charged leptons are required to \BJ{fulfill cuts on transverse momentum, rapidity, and separation in the rapidity-azimuthal angle separation, }
        \begin{align}
        \label{cut:1}
         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
        \end{align}
        %
    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos, is required to be
        \begin{align}
        \label{cut:2}
          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
        \end{align}
        %
    \item QCD partons (quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. %Jets are required to have
    \BJ{We impose cuts on the jets' transverse momenta, rapidities, and their separation from leptons, } 
        \begin{align}
        \label{cut:3}
         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
        \end{align}
        VBS cuts are applied on the two jets with largest transverse-momentum, unless otherwise stated. In particular, we impose a cut on the 
         in\-vari\-ant mass of the di-jet system,  as well as on the rapidity-separation of the two jets,          \begin{align}
        \label{cut:4}
         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5, 
        \end{align}
        if not explicitly stated otherwise. 
        %
    \item When EW corrections are computed, real photons and charged fermions are clustered together using the anti-$k_T$ algorithm with
        radius parameter $R=0.1$. In this case, leptons and quarks are understood as {\it dressed fermions}.
\end{itemize}

>>>>

The renormalisation and factorisation scales are set to the dynamical scale
%
\begin{equation}
\label{eq:defscale}
 \mu_{\rm ren} = \mu_{\rm fac} = \sqrt{p_{\rm T, j_1}\, p_{\rm T, j_2}}, 
\end{equation}
%
defined via the transverse momenta of the two hardest identified jets.  
This choice of scale has been shown to provide stable NLO-QCD predictions \cite{Denner:2012dz}.

@@

\begin{itemize}
    \item The two same-sign charged leptons are required to fulfill cuts on transverse momentum, rapidity, and separation in the rapidity-azimuthal angle separation, 
        \begin{align}
        \label{cut:1}
         \ptsub{\Pl} >  20\GeV,\qquad |y_{\Pl}| < 2.5, \qquad \Delta R_{\Pl\Pl}> 0.3\,.
        \end{align}
        %
    \item The total missing transverse energy, computed from the vectorial sum of the transverse momenta of the two neutrinos, is required to be
        \begin{align}
        \label{cut:2}
          \etsub{\text{miss}}=p_{\rm T, miss} >  40\GeV\,.
        \end{align}
        %
    \item QCD partons (quarks and gluons) are clustered together using the anti-$k_T$ algorithm~\cite{Cacciari:2008gp} with distance parameter $R=0.4$. %Jets are required to have
    We impose cuts on the jets' transverse momenta, rapidities, and their separation from leptons,  
        \begin{align}
        \label{cut:3}
         \ptsub{\Pj} >  30\GeV, \qquad |y_\Pj| < 4.5, \qquad \Delta R_{\Pj\Pl} > 0.3 \,.
        \end{align}
        VBS cuts are applied on the two jets with largest transverse-momentum, unless otherwise stated. In particular, we impose a cut on the 
         in\-vari\-ant mass of the di-jet system,  as well as on the rapidity-separation of the two jets,          \begin{align}
        \label{cut:4}
         m_{\Pj \Pj} >  500\GeV,\qquad |\Delta y_{\Pj \Pj}| > 2.5, 
        \end{align}
        if not explicitly stated otherwise. 
        %
    \item When EW corrections are computed, real photons and charged fermions are clustered together using the anti-$k_T$ algorithm with
        radius parameter $R=0.1$. In this case, leptons and quarks are understood as {\it dressed fermions}.
\end{itemize}
